Group 9 Presentation

### 2021-12-08 boosting.Rmd
Lot of formatting on the presentation, removed last slide into one Results slide, added boostings, bagging is now broken.

---
title: "Boosting"
author: "Henrique"
output: html_notebook
---

@@

set.seed(445)
lambda=seq(from=0,to=1,length.out=100)

tmse<-0

@@

gbm_grid =  expand.grid(interaction.depth = 1:5,
                        n.trees = (1:6) * 500,
                        shrinkage = c(0.001, 0.01, 0.1),
                        n.minobsinnode = 10)

@@

```{r}
boost <- gbm(HeartDisease~.,data=train,n.trees=500,shrinkage=0.01,interaction.depth = 1 ,distribution = "bernoulli")

@@

summary(boost)

>>>>

@@ -1,70 +0,0 @@
---
title: "Boosting"
author: "Henrique"
output: html_notebook
---

@@

@@

gbm_grid =  expand.grid(interaction.depth = 1:5,
                        n.trees = (1:5) * 200,
                        shrinkage = c(0.01,0.015,0.1),
                        n.minobsinnode = 10)

@@

```{r}
boost <- gbm(HeartDisease~.,data=train,n.trees=600,shrinkage=0.01,interaction.depth = 2 ,distribution = "bernoulli")

@@

```{r}
summa<-summary(boost)
```

```{r}
ggplot(summa)+geom_col(aes(x=var,y=rel.inf,fill=var))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())+guides(fill="none")
```

### 2021-12-08 presentation.Rmd
Lot of formatting on the presentation, removed last slide into one Results slide, added boostings, bagging is now broken.

library(ISLR)
library(leaps)
library(tidyr)
library(dplyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)
library(reprtree)
library(MASS)
library(e1071)

@@

Jorie's LDA

@@

predicted2 <- ifelse(rf>0.5,1,0)

@@

rf_fit

@@

- Variable importance shows.

```{r}
ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy,fill=variables))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())
```

## Representative Tree
- Following the paper by  Banerjee, et al.(2011) and the package reprtree we can get a representative tree from the random forest.
- This tree is calculated using a measure of similarity in which 2 trees are similar if they have the same prediction for all observations.
- Using this idea on the random forest we get the following tree:

## Tree
```{r fig.height=7, fig.width=15, message=FALSE, warning=FALSE,echo=FALSE}
reptree <- ReprTree(rf_fit, train, metric='d2')

@@

Jorie's SVM

@@

table(test$HeartDisease, preds)
```

## (the new thing)

Henrique's new thing insted of PCA

@@

Henrique's Logisic Regression

```{r}
model_glm = glm(HeartDisease ~ ., data = train, family = "binomial")
#summary(model_glm)

@@

 #MSE

@@

Jories's Boosting

@@

## Bagging
```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}

@@

#Confusion Matrix
predict_bag <- predict(bagging, newdata = test)
predicted_bag <- ifelse(predict_bag>0.5,1,0)
confm_bag<-table(predict_bag,test$HeartDisease)
confm_bag

@@

#sort variable importance descending
VI_plot <- VI[order(VI$imp.0, decreasing=TRUE),]

@@

ggplot(VI_plot)+geom_col(aes(x=(rownames(VI_plot)),y=imp.0,fill=rownames(VI_plot)))+coord_flip()+guides(fill=FALSE)+
  labs(x="Variable Name",y="Importance")

## Comparision of all method's MSE

Chart with all MSE

```{r}
library(knitr)
df1 = data.frame(Method = c('LDA', 'RF', 'SVM', 'new THING', 'Logistic Regression', 'Boosting', 'LASSO', 'PLS', 'Bagging'),  MSE = c(0,0,0,0,0.1498638,0,0,0.1054 ,0.1165492))

@@

## Conclusion

the METHOD worked best, with an MSE of SOMETHING

>>>>

library(ISLR)
library(leaps)
library(tidyr)
library(dplyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)
library(reprtree)
library(MASS)
library(e1071)
library(gbm)

@@

@@

@@

overall_RF <- (confm2[1,1]+confm2[2,2])/sum(confm2)
rf_fit

@@

- ST_Slope
-

```{r}
ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy,fill=variables))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())+guides(fill="none")
```

## Representative Tree
- Following the paper "Identifying representative Trees From Ensembles"  by  Banerjee, et al.(2011) and the package reprtree we can get a representative tree from the random forest.

- This tree is calculated using a measure of similarity, in which 2 trees are similar if they have the same prediction for all observations.

- The representative tree is then choosen based on its averaged similarity between all other trees.

- Using this idea on the random forest we get the following tree:

## Representative Tree Plot
```{r fig.height=7, fig.width=15, message=FALSE, warning=FALSE,echo=FALSE}
reptree <- ReprTree(rf_fit, train, metric='d2')

@@

@@

table(predicted=preds,true=test$HeartDisease)

overall_SVM <- acc

paste("Accuracy", acc)
```

@@

```{r}
model_glm = glm(HeartDisease ~ ., data = train, family = "binomial")
summary(model_glm)

@@

overall_logit <- (confm2[1,1]+confm2[2,2])/sum(confm2)

@@

train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)

test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)

set.seed(445)

oob = trainControl(method = "oob")
cv_5 = trainControl(method = "cv", number = 5)

gbm_grid =  expand.grid(interaction.depth = 1:5,
                        n.trees = (1:5) * 200,
                        shrinkage = c(0.01,0.015,0.1),
                        n.minobsinnode = 10)

gbm_tune = train(as.factor(HeartDisease) ~ ., data = train,
                      method = "gbm",
                      trControl = cv_5,
                      verbose = FALSE,
                      tuneGrid = gbm_grid)

plot(gbm_tune)

```{r}
boost <- gbm(HeartDisease~.,data=train,n.trees=600,shrinkage=0.01,interaction.depth = 2 ,distribution = "bernoulli")

boostpred = ifelse(predict(boost,test, n.trees = 500, "response") > 0.5, "1", "0")

confboost<-table(predicted = boostpred, actual = test$HeartDisease)
confboost
error<-(confboost[1,1]+confboost[2,2])/sum(confboost)
overall_boost <- error
```

```{r,include=FALSE}
summa<-summary(boost)
```

```{r}
ggplot(summa)+geom_col(aes(x=var,y=rel.inf,fill=var))+coord_flip()+labs(y="Relative Influence", x= " Variable")+guides(fill="none")
```

@@

## Bagging
```{r,echo=FALSE,warning=FALSE,fig.width=6,fig.height=3}
train <- read.csv("train.csv")
test <- read.csv("test.csv")

train$ChestPainType <- as.factor(train$ChestPainType)
train$Sex <- as.factor(train$Sex)
train$FastingBS <- as.factor(train$FastingBS)
train$RestingECG <- as.factor(train$RestingECG)
train$ExerciseAngina <- as.factor(train$ExerciseAngina)
train$ST_Slope <- as.factor(train$ST_Slope)

test$ChestPainType <- as.factor(test$ChestPainType)
test$Sex <- as.factor(test$Sex)
test$FastingBS <- as.factor(test$FastingBS)
test$RestingECG <- as.factor(test$RestingECG)
test$ExerciseAngina <- as.factor(test$ExerciseAngina)
test$ST_Slope <- as.factor(test$ST_Slope)

@@

#Confusion Matrix
predict_bag <- predict(bagging, newdata = test)
predicted_bag <- ifelse(predict_bag>0.5,1,0)
confm_bag<-table(predict_bag,test$HeartDisease)

@@

#sort variable importance descending
#VI_plot <- VI[order(VI$imp.0, decreasing=TRUE),]

@@

ggplot(VI)+geom_col(aes(x=var,y=Overall,fill=var))+coord_flip()+guides(fill=FALSE)+
  labs(x="Variable Name",y="Importance")
```

## Results

- What method should be choosen?

```{r}
library(knitr)
df1 = data.frame(Method = c("Logistic Regression","LDA","KNN","LASSO","Bagging","Random Forest","Boosting","SVM"),  MSE = c(overall_logit,overall_LDA,overall_knn_1,overall_lasso,overall_bag,overall_RF,overall_boost,overall_SVM))

@@
